Probabilistic Catalogs for Crowded Stellar Fields

### 2012-10-31 paper/ms.tex
Some editing of appendices

%\section{Pixel Convolved PSF}
%{\bf Do people need to be schooled on this? I did...}
%Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
%this image gives rise to the observed data. First, it is convolved with a
%PSF $g(\delta_x, \delta_y)$ (assumed normalized to 1) to give the blurred image:
%\begin{eqnarray}
%f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
%g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
%\end{eqnarray}
%Then, we observe the blurred image with a certain pixellation. Consider a pixel.
%The true flux $F$ within the pixel is:
%\begin{eqnarray}
%F &=& \iint_{\rm pixel} f_{\rm blurred}(x, y) \,dx'\,dy'\\
%&=& \iint f_{\rm blurred}(x, y)\mathbbm{1}\left[(x,y) \in \textnormal{pixel}
%\right] \,dx\,dy \label{pixel}
%\end{eqnarray}
%Now consider $F$ as a function of the central location $(x_c, y_c)$ of the
%pixel.

\section{Usage}
Software can be obtained from {\tt http://github.com/dfm/star-field/}

\section{Proposal Distributions}

\begin{table}\footnotesize
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameter & Proposal & Notes\\
\hline
$N$ & $N \to N + \delta_N$ & Generate $\delta_N$ new stars from prior given
$\beta$\\
$N$ & $N \to N - \delta_N$ & Remove $\delta_N$ stars at random\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Move stars' fluxes along with
$\beta$\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Stars' fluxes fixed, put extra
term in acceptance probability \\
$(x_i,y_i)$ & $(x_i,y_i) \to (x_i,y_i)+(\delta_x, \delta_y)$ & Can move $>1$ star
in a single step \\
$f$ & $f \to f + \delta_f$ & Can move $>1$ stars' fluxes in a single step\\
\hline
\end{tabular}
\end{center}
\caption{All $\delta$ parameters are drawn from multi-scale distibutions such
that the largest steps are of order the prior width, and the smallest steps
are of order $10^{-6}$ times the prior width.\label{proposals}}
\end{table}

See Table~\ref{proposals} for a list of current proposal distributions.

>>>>

%\section{Pixel Convolved PSF}
%{\bf Do people need to be schooled on this? I did...}
%Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
%this image gives rise to the observed data. First, it is convolved with a
%PSF $g(\delta_x, \delta_y)$ (assumed normalized to 1) to give the blurred image:
%\begin{eqnarray}
%f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
%g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
%\end{eqnarray}
%Then, we observe the blurred image with a certain pixellation. Consider a pixel.
%The true flux $F$ within the pixel is:
%\begin{eqnarray}
%F &=& \iint_{\rm pixel} f_{\rm blurred}(x, y) \,dx'\,dy'\\
%&=& \iint f_{\rm blurred}(x, y)\mathbbm{1}\left[(x,y) \in \textnormal{pixel}
%\right] \,dx\,dy \label{pixel}
%\end{eqnarray}
%Now consider $F$ as a function of the central location $(x_c, y_c)$ of the
%pixel.
%\section{Usage}
%Software can be obtained from {\tt http://github.com/dfm/star-field/}

\section{Proposal Distributions}
To implement Metropolis-Hastings moves for the space of possible catalogs,
proposal distributions are required. See Table~\ref{proposals} for a list of
proposal distributions used in this study.

\begin{table}\footnotesize
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameter & Proposal & Notes\\
\hline
$N$ & $N \to N + \delta_N$ & Generate $\delta_N$ new stars from
$p(x, y, f|\beta)$.\\
$N$ & $N \to N - \delta_N$ & Remove $\delta_N$ stars, chosen at random\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Transform
stars' fluxes correspondingly\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Fix stars' fluxes, put extra
term in acceptance probability \\
$(x_i,y_i)$ & $(x_i,y_i) \to (x_i,y_i)+(\delta_x, \delta_y)$ & Can move $>1$ star
in a single step \\
$f$ & $f \to f + \delta_f$ & Can move $>1$ stars' fluxes in a single step\\
\hline
\end{tabular}
\end{center}
\caption{All $\delta$ parameters are drawn from multi-scale distibutions such
that the largest steps are of order the prior width, and the smallest steps
are of order $10^{-6}$ times the prior width.\label{tab:proposals}}
\end{table}
